New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?

### 2024-06-25 02_paper/02_study/02_fitbit paper/fitbit_paper_elsevier/FitBit_elsevier/FitBit_elsevier.Rmd
tabellen

  <!-- https://tinyurl.com/ybremelq -->
keywords: 
  - heart rate
  - photoplethysmography
  - wearable electronic device
  - teaching
journal: "Computers & Education"
date: "`r Sys.Date()`"
classoption: preprint, 3p, authoryear
bibliography: r-references.bib
linenumbers: false
numbersections: true
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: natbib
header-includes:
  - \usepackage{tabularx}
---

@@

library(needs)
needs(ltm,
      broom,
      ppcor,
      jtools,
      lm.beta,
      tidyverse,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      viridis, 
      stargazer)
```

@@

```{r, include=FALSE}

@@

df_desc_hr <- desc_hr_phases |> 
  mutate(across(everything(),
                ~ paste(.,
                        desc_hr_phases_std[[cur_column()]],
                        sep = "/")
                )
         ) #|> 
  # # rename(`\textit{M} HR` = `M HR`,
  #        # `\textit{SD} HR` = `SD HR`,
  #        # `\textit{Min}` = `Min`,
  #        `\textit{Max}` = `Max`,
  #       `\textit{Interval}` = Interval)

@@

names(df_desc_hr) <- paste0("\\textit{", names(df_desc_hr),"}")

stargazer(df_desc_hr,
          type = 'latex',
          out = 'tab_1.tex',
          summary = FALSE,
          rownames = FALSE,
          table.placement = 'h',
          align = FALSE
          ) -> tab_1

pattern <- "textit\\\\\\{([^}]*)\\\\\\}"
replacement <- "\textit{\\1}"

# Anwenden des Regex
tab_1_new <- str_replace_all(tab_1, pattern, replacement)

paste(tab_1_new, collapse = '')

writeLines(tab_1_new, 'tab_1.tex')

>>>>

  <!-- https://tinyurl.com/ybremelq -->
keywords: 
  - heart rate
  - photoplethysmography
  - wearable electronic device
  - teaching
journal: "Computers & Education"
date: "`r Sys.Date()`"
classoption: preprint, 3p, authoryear
bibliography: r-references.bib
linenumbers: false
numbersections: true
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: natbib
header-includes:
  - \usepackage{tabularx}
  - \usepackage{threeparttable}
  - \usepackage{booktabs}
---

@@

library(needs)
needs(ltm,
      broom,
      ppcor,
      jtools,
      lm.beta,
      tidyverse,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      viridis, 
      stargazer,
      papaja)
```

@@

```{r table_1, include=FALSE}

@@

df_desc_hr <- desc_hr_phases |> 
  mutate(across(everything(),
                ~ paste(.,
                        desc_hr_phases_std[[cur_column()]],
                        sep = "/")
                )
         )

@@

tab_1 <- apa_table(df_desc_hr,
                   placement = 'h',
                   )

writeLines(tab_1, 'tab_1.tex')
